% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{cv-style}          % Add 'print' as an option into the square bracket to remove colours from this template for printing. 
                                    % Add 'espanol' as an option into the square bracket to change the date format of the Last Updated Text
\usepackage{tikz}
\definecolor{frontColor}{rgb}{0.22,0.45,0.70}% light blue
\definecolor{backColor}{RGB}{200,200,200}% grey
\newcommand{\grade}[1]{%
    \begin{tikzpicture}
    \clip (1em-.4em,-.35em) rectangle (5em +.5em ,1em);
    \foreach \x in {1,2,...,5}{
        \path[{fill=backColor}] (\x em,0) circle (.35em);
    }
    \begin{scope}
    \clip (1em-.4em,-.35em) rectangle (#1em +.5em ,1em);
    \foreach \x in {1,2,...,5}{
        \path[{fill=frontColor}] (\x em,0) circle (.35em);
    }
    \end{scope}

    \end{tikzpicture}%
}

\sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut 

\begin{document}

\header{Rohit }{Rana }           % Your name
\lastupdated

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------

\begin{aside}
%
\section{Contact}
New Delhi, IN
~
Mobile no:
+91 8800211079
~
Email:
rohitrana.r07@ducic.ac.in
%
\section{Industry Knowledge}
\begin{flushright}
Front End Web Development:\\ \grade{5}  
Back End Web Development:\\ \grade{4}
AR/VR:\\ \grade{3.5}  
Machine learning:\\ \grade{2}
\end{flushright}
%
\section{Languages \&
   Frameworks}
C++ | Android | Nodejs
Python | PHP | MySQL
HTML5 | CSS3
JavaScript | Angular 2+
AJAX | Bootstrap | C\#
Alexa skill Kit for Nodejs
%

\section{Tools \&
   Technologies}
Git | GitHub | VS Code
Blender | Plesk 
Firebase | Cpanel
Unity | Android Studio
Amazon Developer Console | Ubantu
%
\end{aside}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{entrylist}
%------------------------------------------------
\entry
  {May-Sept 2018}
  {Analytics2Action}
  {Canada(remote)}
  {\jobtitle{Data Science Intern}\\
  five months experience as Intern of Data Science  and Sentiment Analysis in Analytics2Action}
%------------------------------------------------
\entry
  {Feb-Dec 2018}
  {Kanshiram Welfare Foundation}
  {Delhi, India}
  {\jobtitle{Web Development Intern}\\
  Developing and Managing Non Profit Organization's Website. \\\
  Detailed achievements:
  \begin{itemize}
    \item Get Detail understanding in non commercial Website.
     
     \item Good Knowledge in data Handling and web Hosting.
     
     
  \end{itemize}}
%------------------------------------------------
%------------------------------------------------
\entry
  {Jan 2018-Present}
  {University of Delhi}
  {Delhi, India}
  {\jobtitle{Mixed Reality Researcher}\\
  Introduced innovative ways of learning for Autistic kids. \\\
  Technology Stack:
  \begin{itemize}
    \item  Unity, ARCore, Simmetri, Amazon Sumerian
     
     
  \end{itemize}}
%------------------------------------------------
%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------
\entry
{2013--2016}
{B.Tech {\normalfont in Information Technologies \& Mathematical Innovation}}
{Cluster Innovation Center, University of Delhi}


%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	OTHER QUALIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{Projects}

\begin{entrylist}
%------------------------------------------------
\entry
{May-Sept 2018}
{Sentiment Analysis }
{Analytics2Action}
{Develop a sentiment analysis model to predict sentiment of call center data \newline
https://github.com/Rohit777/sentiment\_analysis}
{\vspace{-0.3cm}}
\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{Feb-2018}
{NGO Website}
{Kanshiram Welfare Foundation}
{Develop non-commercial Website on PHP for Kanshiram Welfare Foundation\newline
http://kanshiramfoundation.org/}
{\vspace{-0.3cm}}
\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{Jan-2019}
{Indoor Navigation}
{Cluster Innovation Center}
{Using Cloud Anchor by Google ARcore i developed a AR based indoor navigation system which will show path to user on Augmented Reality \newline
https://drive.google.com/file/d/1JGzmkIfK\_W2Yyb0JqGTbgFiqwISQdPBw/view?
usp=sharing}
{\vspace{-0.3cm}}
\end{entrylist}
\begin{entrylist}
%------------------------------------------------
\entry
{Mar-2019}
{StudyAR}
{Cluster Innovation Center}
{Developed Augmented Reality based interactive Study material using ARcore and cloud Anchors for student. \newline https://drive.google.com/file/d/1WU6vuJSG0DaE9MA\_JcoxzOqflsHD\_nDn/view?
usp=sharing }
{\vspace{-0.3cm}}


%------------------------------------------------
\end{entrylist}
\begin{entrylist}
%------------------------------------------------
\entry
{Jan-2018}
{AR Book}
{Cluster Innovation Center}
{Developed Augmented Reality Based children alphabet book. \newline https://drive.google.com/file/d/1ky9W1rwxu41pBLlzj9auQZFDkv3RaaEe/view?
usp=sharing }
{\vspace{-0.3cm}}


%------------------------------------------------
\end{entrylist}
\pagebreak
%----------------------------------------------------------------------------------------
%	Achievement  SECTION
%----------------------------------------------------------------------------------------

\section{Achievements}

\begin{entrylist}
\entry
{}
{Hack on Hills 3.0 Winner }
{\newline Winner of North India's one of the Biggest Hackathon Organised by NIT Hamirpur. }
{}

%------------------------------------------------
\end{entrylist}
\begin{entrylist}
\entry
{}
{Co-founder of DreamAR}
{\newline Open Community For Student Who want to Learn and explore the Augmented Reality Development}
{}

%------------------------------------------------
\end{entrylist}



%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}
  \vspace{-0.3cm}
\begin{entrylist}
%------------------------------------------------
\entry
{}
{ Designing Websites:}
{}
{Develop creative design and animation in website}

\end{entrylist}\
\begin{entrylist}
%------------------------------------------------
\entry
{}
{AR/VR}
{}
{Good Knowledge in AR and VR and designed many children AR BOOK.}
\end{entrylist}\
\begin{entrylist}
%------------------------------------------------
\entry
{}
{Deep learning}
{}
{Good Knowledge in deep learning and pytorch.
}

\end{entrylist}\
%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}
  \vspace{-0.2cm}

\begin{entrylist}
%------------------------------------------------
\entry
  {}
  {Good Management skills}
  {}
  {\jobtitle{}\  Excellent Management Skills which require in company}
%------------------------------------------------
\entry
  {}
  {Programming Ability }
  {}
  {\jobtitle{}\  Good programming skills in Python, PHP and JavaScript.}
  
  \entry
  {}
  { Quick Learning Capability}
  {}
  {\jobtitle{}\ Quick learning all the fundamental of the Software Technology    }
  
  \entry
  {}
  {Good in Communication }
  {}
  {\jobtitle{}\  Know two different languages }
  
%------------------------------------------------
%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	Hobby SECTION
%----------------------------------------------------------------------------------------

\section{Hobbies}
  \vspace{-0.2cm}

\begin{entrylist}
%------------------------------------------------

%------------------------------------------------
\entry
  {}
  {Learn about new Web technology }
  {}
  {\jobtitle{}\ Learn about the latest technology which helpful in Industry level development and Improve my programming Skills as well.}
  
  \entry
  {}
  {Learn and Research about new technology related to augmented reality }
  {}
  {\jobtitle{}\ try to learn about all new AR/VR plugins and SDK 
  \begin{itemize}

     
     
  \end{itemize}}
%   \entry
%   {}
%   {Reading Article and tweets }
%   {}
%   {\jobtitle{}\ Go morning walk on daily base. }
  \entry
  {}
  {Attend technological meet up and summit }
  {}
  {\jobtitle{}\ Like GDG, amazon developer summit, hands on workshop... }
  
%------------------------------------------------
%------------------------------------------------

\end{entrylist}


\end{document}
